DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-26 paper/evaluation-drampart.tex
Minor changes to evaluation

Figures \ref{fig:memguard_bandwidth} shows the results.
As clearly can be seen in the figure, limiting the co-runners's memory
bandwidth is effective in protecting the CNN model's performance for
BwRead and BwWrite co-runners. The benefits are especially more
pronounced in case of BwWrite co-runners as we throttle them more the
CNN's performance quickly improves.

>>>>

Figures \ref{fig:memguard_bandwidth} shows the results.
As can clearly be seen in the figure, limiting the co-runners's memory
bandwidth is effective in protecting the CNN model's performance for
BwRead and BwWrite co-runners. The benefits are especially more
pronounced in case of BwWrite co-runners as, when we throttle them more, the
CNN's performance quickly improves.

### 2018-04-26 paper/main.tex

We find that all tested platforms, including the Pi 3, are capable of
supporting the CNN-based real-time control, from 20 Hz up to 100
Hz depending on hardware platform. 
However, we find that shared resource contention remains an
important issue that must be considered in applying CNN models on
shared memory based embedded computing platforms; we observe 
up to 11.6X execution time increase in the CNN based control loop due
to shared resource contention. To protect the CNN workload, we also
evaluate state-of-the-art cache partitioning and memory bandwidth
throttling techniques on the Pi 3. We find that cache partitioning is
ineffective, while memory bandwidth throttling is an effective
solution.
\end{abstract}

>>>>

We find that all tested platforms, including the Pi 3, are capable of
supporting the CNN-based real-time control, from 20 Hz up to 100
Hz, depending on hardware platform. 
However, we find that shared resource contention remains an
important issue that must be considered in applying CNN models on
shared memory based embedded computing platforms; we observe 
up to 11.6X execution time increase in the CNN based control loop due
to shared resource contention. To protect the CNN workload, we also
evaluate state-of-the-art cache partitioning and memory bandwidth
throttling techniques on the Pi 3. We find that cache partitioning is
ineffective, while memory bandwidth throttling is an effective
solution.
\end{abstract}
